Topological Analysis of Bitcoin's Lightning Network

### 2019-01-06 article/main.tex
Random failures

\title{Post-Quantum Verifiable Delay Functions}
\author[1]{Péter Burcsi}
\author[1]{István András Seres}
\author[1]{Dániel A. Nagy}
\affil[1]{Department of Computer Algebra, Eötvös Loránd University}
\begin{document}
\maketitle

@@

\end{abstract}
\keywords{Cryptography, Verifiable delay function, Post-Quantum Cryptography, Cryptocurrency, Ethereum}

\section{Introduction}
\section{Background}
\section{Construction}
\section{Security arguments}
\section{Conclusion}
\section{Acknowledgements}

>>>>

\title{Topological Analysis of Bitcoin's Lightning Network }
\author[1]{István András Seres}
\author[1]{Dániel A. Nagy}
\author[1]{Péter Burcsi}
\affil[1]{Department of Computer Algebra, Eötvös Loránd University}
\begin{document}
\maketitle

@@

\end{abstract}
\keywords{Bitcoin, Lightning Network, Network Topology, Payment Channel Network}

\section{Introduction}
\section{Lightning Network's Topology}
\section{Robustness of LN}
\subsection{Random Failures}
\subsection{Targeted attacks}
\begin{figure}[h]
	\centering
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{vertexConnectivity.png}
		\captionof{figure}{LN's vertex connectivity}
		\label{fig:test1}
	\end{minipage}%
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{edgeConnectivity.png}
		\captionof{figure}{LN's edge connectivity}
		\label{fig:test2}
	\end{minipage}
\end{figure}

\subsection{Fixing LN's resilience against attacks}
percolation threshold
\section{Privacy}
topological anomalies have privacy implications, low usage of tor, even tor can not help
\section{Conclusion}
\section{Acknowledgements}
